---
title: "Univariate Analysis on a test dataset"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    number_sections: true
    theme: journal
---

```{r rmarkdown_libraries, echo=FALSE}
#install.packages(c("janitor", "dplyr", "ggplot2", "lubridate", "lsmeans", 
#                   "tidyr", "broom", "DT", "stringi", "ggcorrplot", 
#                   "knitr", "plotly", "heatmaply"))
```

```{r rmarkdown_setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 9.25, fig.height=6)
options(knitr.duplicate.label = "allow")
withr::local_options(list(htmltools.preserve.raw = FALSE))

```


```{r libraries}
# library(dataiku) # REMOVED FOR LOCAL USE
library(janitor)
library(dplyr)
library(ggplot2)
library(lubridate)
library(lsmeans)
library(tidyr)
library(broom)
library(DT)
library(stringi)
library(ggcorrplot)
library(knitr)
library(plotly)
library(DT)
library(heatmaply)

```

```{r configuration, echo=FALSE}
# ==============================================================================
# DATASET AND VARIABLE CONFIGURATION (CENTRALIZED CONTROL)
# Modify the values below to adapt the script to a new file
# ==============================================================================

# 1. File Path (Local CSV)
# Provide the relative or absolute path to your CSV file
input_file_path <- "synthetic_vaccine_batch_data.csv" 

# 2. Definition of "Pillar" Columns
# WARNING: Use names as they will appear after automatic cleaning (janitor::clean_names)
# i.e.: all lowercase, no accents, spaces replaced by underscores (_)
col_target <- "vaccine_yield_g_l"              # Quantitative target variable (Y)
col_date   <- "production_date"            # Date variable (Temporal X)
col_id     <- "id_lot"                     # Unique identifier (for chronological order)

# 3. Time Filtering Parameters
# Leave NULL or "" if you do not want to filter on a specific bound
filter_start_date <- "2024-01-01"  # Expected format: "YYYY-MM-DD"
filter_end_date   <- "2026-12-31"  # Expected format: "YYYY-MM-DD"

# 4. Date format in the original CSV file 
# Examples: "%d-%m-%Y" (for 31-01-2024) or "%Y-%m-%d" (for 2024-01-31)
input_date_format <- "%d-%m-%Y"

# ==============================================================================
```


```{r dataset_upload, results='asis'}

# Target variable assignment from config
vy <- col_target

# Load and clean dataset (LOCAL IMPORT)
# check.names=F avoids R renaming columns (replacing spaces with dots) before clean_names does its job
df_raw <- read.csv(input_file_path, sep = ";", dec = ".", check.names = FALSE, stringsAsFactors = FALSE) %>%
  janitor::clean_names()

# Check if columns exist after cleaning names
required_cols <- c(col_target, col_date, col_id)
if(!all(required_cols %in% names(df_raw))){
  missing_cols <- setdiff(required_cols, names(df_raw))
  stop(paste("ERREUR CRITIQUE : Les colonnes suivantes sont introuvables après le nettoyage des noms (clean_names) :", 
             paste(missing_cols, collapse=", "), 
             ". Vérifiez l'orthographe dans le bloc CONFIGURATION."))
}

# Remove rows where target variable is missing
df_filtered <- df_raw %>%
  filter(!is.na(.data[[vy]]))

# --------------------------------------------- #
# Parse date column (Robust Normalization)
# --------------------------------------------- #
if (col_date %in% colnames(df_filtered)) {
  # Utilisation de lubridate pour gérer les formats mixtes (/, -, année 2 ou 4 chiffres)
  # orders = c("dmy", "ymd") tente d'abord Jour-Mois-Année, puis Année-Mois-Jour
  df_filtered <- df_filtered %>%
    mutate(!!as.symbol(col_date) := as.Date(lubridate::parse_date_time(
      .data[[col_date]], 
      orders = c("dmy", "dmY", "ymd", "Ymd")
    )))
}

# --------------------------------------------- #
# Remove rows with missing or invalid dates
# --------------------------------------------- #
df_filtered <- df_filtered %>%
  filter(!is.na(.data[[col_date]]))

# --------------------------------------------- #
# Filter by Date Range (Start / End) - NEW STEP
# --------------------------------------------- #
if(!is.null(filter_start_date) && filter_start_date != ""){
  df_filtered <- df_filtered %>%
    filter(.data[[col_date]] >= as.Date(filter_start_date))
  cat(paste("Date Filter active : Data utilized from", filter_start_date, "\n"))
}

if(!is.null(filter_end_date) && filter_end_date != ""){
  df_filtered <- df_filtered %>%
    filter(.data[[col_date]] <= as.Date(filter_end_date))
  cat(paste("Date Filter active : Data utilized to", filter_end_date, "\n"))
}

cat(paste0("\nNumber of rows kept after date filter : ", nrow(df_filtered), "\n\n"))

# --------------------------------------------- #
# Determine true chronological order of lots
# --------------------------------------------- #
lot_order_df <- df_filtered %>%
  group_by(!!as.symbol(col_id)) %>%
  summarise(min_date = min(!!as.symbol(col_date), na.rm = TRUE), .groups = "drop") %>%
  arrange(min_date)

ordered_lots <- lot_order_df %>% pull(!!as.symbol(col_id))

# --------------------------------------------- #
# Apply ordered factor to lots
# --------------------------------------------- #
df_filtered <- df_filtered %>%
  mutate(!!as.symbol(col_id) := factor(.data[[col_id]], levels = ordered_lots))

# --------------------------------------------- #
# Detect and remove constant columns
# --------------------------------------------- #
cols_constant <- df_filtered %>%
  summarise(across(everything(), ~ n_distinct(., na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "column", values_to = "n_unique") %>%
  filter(n_unique <= 1) %>%
  pull(column)

df_analysis <- df_filtered %>%
  select(-all_of(cols_constant)) %>%
  mutate(!!as.symbol(col_id) := factor(.data[[col_id]], levels = ordered_lots))  # reapply to ensure order

# --------------------------------------------- #
# Display removed columns
# --------------------------------------------- #
if (length(cols_constant) > 0) {
  cat("### Removed Constant Columns\n\n\n\nThese columns had the same (non-missing) value across all rows and were removed from the analysis:\n\n")
  print(knitr::kable(data.frame(Constant_Columns_Removed = cols_constant)), row.names = FALSE)
} else {
  cat(" No constant columns detected among non-missing rows for the target variable.\n")
}

```

```{r early_param_definitions, include=FALSE}
# Defines IDs based on configuration variables
vparams_id <- c(col_id, col_date)

vparam_quantitative <- df_analysis %>%
  select(where(is.numeric)) %>%
  colnames()
```

```{r functions_set_up}

func_clean_title = function(v){return(gsub("_", " ", v))}
# cleanvar = function(v){return(gsub("_", " ", v))}

print_summary_loop = function(s){
  length_element <- length(capture.output(s))
  sapply(1:length_element, function(j) cat(paste0("`", ". ", capture.output(s)[j]), "`  \n"))
}

function_title <- function(vtitle, vheader_level = 4){
  vtitle_return <- paste(paste(rep("#",vheader_level), collapse = ""), vtitle, "\n", collapse=" ")
  return(cat(vtitle_return))
}

function_comment <- function(vcomment){
  if(!is.null(vcomment)){cat(vcomment); cat("\n\n")}
}

print_summary_loop = function(s){
  length_element <- length(capture.output(s))
  sapply(1:length_element, function(j) cat(paste0("`", ". ", capture.output(s)[j]), "`  \n"))
}

theme_plot <- theme_bw() +  
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )


generate_df_glance_only <- function(dfunc, vy, vparams_id, vparam_quantitative) {
  df_univariate_quanti <- dfunc %>%
    select(any_of(c(vparams_id, vparam_quantitative, vy)))

  df_melt <- df_univariate_quanti %>%
    pivot_longer(cols = -any_of(c(vparams_id, vy))) %>%
    group_by(name) %>%
    filter(!all(is.na(value))) %>%
    filter(!is.na(value)) %>%
    filter(!is.na(!!as.symbol(vy))) %>%
    ungroup()

  df_glance <- df_melt %>%
    nest_by(name) %>%
    mutate(mod = list(lm(as.formula(paste(vy, "~ value")), data = data, na.action=na.exclude))) %>%
    reframe(glance(mod)) %>%
    clean_names() %>%
    arrange(desc(adj_r_squared)) %>%
    mutate(
      significativity = case_when(
        p_value <= 0.05 ~ "significant",
        p_value > 0.05 ~ "not significant"
      ),
      name = gsub("_", " ", name),
      adj_r_squared = round_half_up(adj_r_squared * 100, 0)
    )

  assign("df_glance", df_glance, envir = .GlobalEnv)
}

vx_runchart <- col_id  # Linked to config variable
vntick <- 2
vy <- col_target       # Linked to config variable
vy_txt <- func_clean_title(vy)

```


```{r runchart_function}

runchart_function = function(
    dfunc_runchart,
    vx_runchart,
    vy_runchart,
    vmanufacturing_date = NULL,
    vcolor_runchart = NULL,
    vfacetx_runchart = ".",
    vfacety_runchart = ".",
    bool_show_color_legend = F,
    bool_facet_scale = "free_y",
    bool_vertical_line_per_year = T,
    vtitle = NULL,
    vntick = 5
){
  
  vy_runchart_txt <- func_clean_title(vy_runchart)
  vx_runchart_txt <- func_clean_title(vx_runchart)
  vx_runchart_class <- dfunc_runchart %>% 
    distinct(!!as.symbol(vx_runchart)) %>% 
    pull() %>% 
    class()
  
  prunchart <- ggplot(data = dfunc_runchart, aes_string(x = vx_runchart, y = vy_runchart, group = 1)) + 
    geom_point(aes_string(color = vcolor_runchart), show.legend = bool_show_color_legend) + 
    geom_line(color = "grey", linetype = "dotted") + 
    facet_grid(reformulate(vfacetx_runchart, vfacety_runchart), scales = bool_facet_scale,
               labeller = label_wrap_gen(width = 20, multi_line = TRUE)) + 
    theme_plot + 
    ylab(vy_runchart_txt) + 
    xlab(vx_runchart_txt) + 
    ggtitle(vtitle)
  
  if(vx_runchart_class %in% c("character", "factor")){
    
    vx_lot <-  dfunc_runchart %>% 
      distinct(!!as.symbol(vx_runchart)) %>% 
      pull()
      
    prunchart <- prunchart +
      scale_x_discrete(breaks = vx_lot[seq(1, length(vx_lot), vntick)])

  }
  
  if(is.null(vmanufacturing_date) & bool_vertical_line_per_year){
      cat("The variable 'bool_vertical_line_per_year' is set to TRUE",
          "But there were no variable 'vmanufacturing_date' variable set up.",
          "\n")
    }
    
  return(prunchart)
  
}


```

# Introduction

## Descriptive analysis for all parameters

The aim of this report is to identify the most impactful parameters on `r vy_txt` for each parameter.

### Run chart 
 
This first section introduces the run chart for this parameter overtime :

```{r common_runchart}

runchart_function(
    dfunc_runchart = df_analysis,
    vx_runchart = col_id,            # Uses config
    vy_runchart = vy,
    vmanufacturing_date = col_date,  # Uses config
    vcolor_runchart = NULL,
    #vcolor_runchart = NULL,
    vfacetx_runchart = ".",
    vfacety_runchart = ".",
    bool_show_color_legend = F,
    bool_facet_scale = "free_y",
    bool_vertical_line_per_year = T,
    vtitle = NULL,
    vntick = 5
)

cat("\n\n")

```

### Correlation plot with the target variable (above |0.2|)

This plot shows the Pearson correlation between each numeric parameter and the target variable `r func_clean_title(vy)`.


```{r correlation plot}

df_corr_numeric <- df_analysis %>%
  select(where(is.numeric)) %>%
  select(-any_of(vy))

# Check to ensure numeric columns exist
if(ncol(df_corr_numeric) > 0) {
  correlations <- sapply(df_corr_numeric, function(x) cor(x, df_analysis[[vy]], use = "complete.obs"))
  
  cor_df <- data.frame(
    Variable = names(correlations),
    Correlation = correlations
  ) %>%
    mutate(abs_corr = abs(Correlation)) %>%
    filter(abs_corr > 0.2) %>%
    arrange(Correlation) %>%
    mutate(
      Short_ID = paste0("Var", sprintf("%02d", row_number())),
      Display = paste0(Short_ID, ": ", ifelse(nchar(Variable) > 45, paste0(substr(Variable, 1, 42), "..."), Variable)),
      hover_txt = paste0("<b>", Variable, "</b><br>Correlation: ", round(Correlation, 3))
    )
  
  if(nrow(cor_df) > 0){
    cor_df$Display <- factor(cor_df$Display, levels = cor_df$Display)
    
    n_vars <- nrow(cor_df)
    plot_height <- max(400, n_vars * 30)
    
    plot_ly(
      data = cor_df,
      x = ~Correlation,
      y = ~Display,
      type = 'bar',
      orientation = 'h',
      text = ~hover_txt,
      hoverinfo = 'text',
      marker = list(
        color = ~Correlation,
        colorscale = 'RdBu',
        reversescale = TRUE,
        line = list(color = "black", width = 0.5)
      )
    ) %>%
      layout(
        title = list(text = paste("Correlation with", func_clean_title(vy)), x = 0),
        height = plot_height,
        margin = list(l = 50, r = 30, t = 50, b = 50),
        xaxis = list(title = "Pearson correlation", zeroline = TRUE),
        yaxis = list(title = "", automargin = TRUE, showticklabels = FALSE)
      )
  } else {
    cat("No variables found with correlation > 0.2")
  }
} else {
  cat("Not enough numeric variables for correlation analysis.")
}


cat("\n\n")
```
<br><br><br>
<br><br><br>
<br><br><br>
<br><br><br>


<br><br><br>

```{r setup_df_glance_for_table, include=FALSE}
generate_df_glance_only(
  dfunc = df_analysis,
  vy = vy,
  vparams_id = vparams_id,
  vparam_quantitative = vparam_quantitative
)
```

### Interactive table of univariate regressions

```{r r2_navigation_table}
# Vérifie si les régressions ont bien été calculées
if(exists("df_glance") && nrow(df_glance) > 0) {
  
  # Préparation du tableau pour l'affichage
  df_table_display <- df_glance %>%
    arrange(desc(adj_r_squared)) %>%
    mutate(
      # Création des liens HTML pour la navigation interne
      Parameter = paste0('<a href="#', gsub(" ", "-", stringi::stri_trans_general(name, "Latin-ASCII")), '">', name, '</a>'),
      `Adjusted R² (%)` = adj_r_squared
    ) %>%
    select(Parameter, `Adjusted R² (%)`, significativity)
  
  # Affichage du tableau interactif
  DT::datatable(
    df_table_display,
    escape = FALSE, # Important pour que les liens HTML fonctionnent
    rownames = FALSE,
    options = list(
      pageLength = 10,
      scrollX = TRUE,
      order = list(list(1, 'desc'))
    )
  ) %>%
    DT::formatStyle(
      columns = c('Adjusted R² (%)', 'significativity'),
      backgroundColor = DT::styleEqual(
        c("significant", "not significant"),
        c("#00BFC4", "#F8766D")
      )
    )
} else {
  cat("Aucune régression calculée ou le tableau est vide.")
}
```


<br><br><br>



### Global correlation table (above|0.5|) 
```{r corr_data, echo=FALSE}

# 1. Sélection des variables numériques valides
df_corr <- df_analysis %>%
  select(where(is.numeric)) %>%
  select_if(~ sd(., na.rm = TRUE) > 0) %>%
  select_if(~ sum(!is.na(.)) >= 3)

# 2. Calcul de la matrice de corrélation pairwise
cor_mat <- tryCatch({
  cor(df_corr, use = "pairwise.complete.obs")
}, error = function(e) NULL)

if (is.null(cor_mat) || ncol(cor_mat) < 2) {
  cat("Not enough numeric data to compute correlations.")
} else {
  # 3. Extraire les paires de corrélations
  cor_df <- as.data.frame(as.table(cor_mat)) %>%
    rename(Var1 = Var1, Var2 = Var2, Correlation = Freq) %>%
    filter(Var1 != Var2) %>%
    mutate(abs_corr = abs(Correlation)) %>%
    rowwise() %>%
    mutate(key = paste(sort(c(Var1, Var2)), collapse = "_")) %>%
    ungroup() %>%
    distinct(key, .keep_all = TRUE) %>%
    select(-key)

  # 4. Garder les plus fortes corrélations
  top_cor <- cor_df %>%
    filter(abs_corr >= 0.5) %>%
    arrange(desc(abs_corr)) %>%
    mutate(Correlation = round(Correlation, 3))

  # 5. Affichage interactif
  if (nrow(top_cor) == 0) {
    cat("No strong correlations (|r| ≥ 0.5) found.")
  } else {
    datatable(
      top_cor %>% select(Var1, Var2, Correlation),
      caption = "Top correlated variable pairs (|r| ≥ 0.5)",
      options = list(pageLength = 10, autoWidth = TRUE)
    )
  }
}






cat("\n\n")

```
<br><br><br>

<br><br><br>



```{r functions_for_univariate_quantitative_parameters}

regression_func = function(
  df_reg,
  vx,
  vy,
  vx_runchart = col_id, # Uses config variable
  vmanufacturing_date = col_date, # Uses config variable
  vcolor_runchart = NULL,
  vntick = 5,
  vheader_level = 3
    ){
  
  
  # --------------------------------------------------------- #
  # Initialisation
  # --------------------------------------------------------- #
  vy_txt <- func_clean_title(vy)
  vx_txt <- func_clean_title(vx)
  vx_runchart_txt <- func_clean_title(vx_runchart)
  vcolor_runchart_txt <- func_clean_title(vcolor_runchart)
  
  df_runchart <- df_reg %>% 
    arrange(!!as.symbol(vmanufacturing_date)) %>% 
    mutate(
      !!as.symbol(vx_runchart) := factor(!!as.symbol(vx_runchart), levels = unique(!!as.symbol(vx_runchart)))#,
      ) %>% 
    pivot_longer(cols = any_of(c(vx, vy))) %>% 
    mutate(name = gsub("_", " ", name))

  function_title(vtitle = func_clean_title(vx), vheader_level = vheader_level)
  
  function_title(vtitle = "Run chart", vheader_level = vheader_level + 1)
  
  cat("The following plot introduces the results of", vx_txt, " by ", vx_runchart_txt,".\n")
  
  prunchart <- runchart_function(
    dfunc_runchart = df_runchart,
    vx_runchart = vx_runchart,
    vy_runchart = "value",
    vmanufacturing_date = vmanufacturing_date,
    vcolor_runchart = NULL,
    #vcolor_runchart = vcolor_runchart,
    vfacetx_runchart = ".",
    vfacety_runchart = "name",
    bool_show_color_legend = F,
    bool_facet_scale = "free_y",
    vtitle = paste0("Run chart of", "\n", vx_txt),
    vntick = vntick
  )
  
  plot(prunchart)
  cat("\n\n")
  
  function_title(vtitle = "Linear regression", vheader_level = vheader_level + 1)
  
  function_title(vtitle = "Regression plot", vheader_level = vheader_level + 2)
  
  cat("The following section introduces the linear correlation between '", 
      vx_txt, "' and '", vy_txt,"'.")
  
  pregplot <- ggplot(data = df_reg, aes_string(x = vx, y = vy)) + 
    geom_point() + 
    geom_smooth(method = "lm", color = "purple") + 
    theme_plot + 
    xlab(vx_txt) + 
    ylab(vy_txt) + 
    ggtitle(paste("Regression plot between", vy_txt, "\nand", vx_txt))
  
  plot(pregplot)
  cat("\n\n")
  
  function_title(vtitle = "Model outputs", vheader_level = vheader_level + 2)
  
  function_title(vtitle = "Summary", vheader_level = vheader_level + 3)
  
  vformula_lm <- paste(vy, "~", vx)
  # m <- lm(formula = as.formula(vformula_lm), data = df_reg)
  
  # to avoid very long names and rendering the reading uneasy,
  # there is a renaming to be done
  m <- lm(formula = as.formula(paste(vy, "~ variable")), 
          data = df_reg %>% rename("variable" = vx))
  s <- summary(m)
  
  invisible(print_summary_loop(s))
  cat("\n\n")
  
  # print(s)
  cat("\n\n")
  
  function_title(vtitle = "Hypotheses checking", vheader_level = vheader_level + 3)
  
  df_resid <- df_reg %>% 
  bind_rows(
      data.frame(
        fitted = m$fitted.values,
        resid = s$residuals
        )
  )

  vy_val <- pretty(df_resid$resid)
  
  pqqplot <- ggplot(data = df_resid, aes(sample=resid)) + 
    geom_qq() + 
    geom_qq_line() +
    theme_plot + 
    ggtitle(paste0("Normal QQ-plot of the residuals\nfrom the linear regression")) + 
    scale_y_continuous(labels = vy_val, breaks = vy_val, limits = range(vy_val))
  
  plot(pqqplot)
  cat("\n\n")
  
  presidfit <- ggplot(data = df_resid, aes(x = fitted, y = resid)) + 
    geom_point() + 
    geom_hline(aes(yintercept = 0), color = "purple") + 
    theme_plot + 
    xlab("Fitted values by the linear regression") + 
    ylab("Residuals") + 
    ggtitle(paste0("Residual vs Fitted values\nfrom the linear regression")) + 
    scale_y_continuous(labels = vy_val, breaks = vy_val, limits = range(vy_val))
  
  plot(presidfit)
  cat("\n\n")
  
}

root_univariate_numeric = function(
    dfunc_univ_quanti = NULL,
    vy = NULL,
    vx_runchart = NULL,
    vcolor_runchart = NULL,
    vparams_id = NULL, 
    vparam_quantitative = NULL,
    vheader_level = 2,
    vntick = 5
){

  function_title(vtitle = "Overall Linear regression overview", vheader_level = vheader_level)
  
  # --------------------------------------------------------- #
  # Dataset preparation
  # --------------------------------------------------------- #
  df_univariate_quanti <- dfunc_univ_quanti %>% 
    select(any_of(c(vparams_id, vparam_quantitative, vy))) 
  
  df_melt <- df_univariate_quanti %>%  
    pivot_longer(cols = -any_of(c(vparams_id, vy))) %>% 
    group_by(name) %>% 
    filter(!all(is.na(value))) %>% 
    filter(!is.na(value)) %>%
    filter(!is.na(!!as.symbol(vy))) %>%
    ungroup()

  vx_param <- df_melt %>% distinct(name) %>% pull()
  
  # --------------------------------------------------------- #
  # All linear models at once to get the adjusted R2
  # --------------------------------------------------------- #
  df_glance <- df_melt %>%
    nest_by(name) %>%
    mutate(mod = list(lm(as.formula(paste(vy, "~ value")), data = data, na.action=na.exclude))) %>%
    reframe(glance(mod)) %>%
    clean_names() %>%
    arrange(adj_r_squared) %>%
    mutate(
      significativity = case_when(
        p_value <= 0.05 ~ "significant",
        p_value > 0.05 ~ "not significant"
      ),
      name = gsub("_", " ", name),
      name = factor(name, levels = unique(name)),
      adj_r_squared = round_half_up(adj_r_squared*100, 0),
    )

  function_title(vtitle = "Adjusted R2 overview", vheader_level = vheader_level + 1)
  
  vx_scale <- c(0, 100, df_glance %>% distinct(adj_r_squared) %>% pull())

  poverview_regression_plot <-  ggplot(
    data = df_glance %>% filter(adj_r_squared > 5), 
    aes(x = adj_r_squared, y = name, color = significativity)) + 
    geom_segment(aes(x = 0, y = name, xend = adj_r_squared, yend = name), 
                 color = "grey", linewidth = 0.2) + 
    geom_point(size = 7) + 
    geom_text(aes(x = adj_r_squared, y = name, label = adj_r_squared), color = 'black', size = 3) +
    xlab("Adjusted R2 (%)") + 
    theme_plot + 
    theme(axis.text.y = element_text(size = 6)) +  
    ggtitle(paste("Overall adjusted R2 (%) plot from linear regression",
                  "\nBetween each parameter and", gsub("_", " ", vy),
                  "\nOnly R2 > 5% are shown")) +
    scale_color_manual(
      values = c(
        "significant" = "#00BFC4",
        "not significant"="#F8766D"
        )
      ) + 
    scale_x_continuous(
      breaks = pretty(vx_scale), 
      labels = pretty(vx_scale), limits = range(vx_scale)
      )
  
  # Ajustement local de la hauteur uniquement pour ce plot
  knitr::opts_chunk$set(fig.height = max(8, length(vx_param) * 1.5))
  suppressWarnings(print(poverview_regression_plot))
  knitr::opts_chunk$set(fig.height = 6)  # réinitialise après
  cat("\n\n")
  # --------------------------------------------------------- #
  # Tableau de navigation vers les régressions individuelles
  # --------------------------------------------------------- #
  assign("df_glance", df_glance, envir = .GlobalEnv)





  
  # --------------------------------------------------------- #
  #  plot
  # --------------------------------------------------------- #

  
  cat("\n\n")
  
  # --------------------------------------------------------- #
  # Apply function for each of the quantitative parameter
  # --------------------------------------------------------- #
  function_title(vtitle = "Analysis by parameter", vheader_level = vheader_level)
  
  for(i in 1:length(vx_param)){
    
    regression_func(
      df_reg = df_univariate_quanti,
      vx = vx_param[i],
      vy = vy,
      vx_runchart = vx_runchart,
      vcolor_runchart = vcolor_runchart,
      vntick = vntick,
      vheader_level = vheader_level + 1,
      vmanufacturing_date = col_date # Uses config variable
    )   
  } 
}


```


```{r functions_for_univariate_qualitative_parameters}

qualitative_analysis_one_parameter = function(
    dfunc_quali_one_analysis,
    vx,
    vy,
    vx_runchart,
    vcolor_runchart = NULL,
    vheader_level = 3,
    vntick = 3,
    vmanufacturing_date = col_date # Uses config variable
    ){
  
  # --------------------------------------------------------- #
  # Initialisation
  # --------------------------------------------------------- #
  vy_txt <- func_clean_title(vy)
  vx_txt <- func_clean_title(vx)
  vx_runchart_txt <- func_clean_title(vx_runchart)
  
  # dfunc_melt_child <- dfunc_quali_one_analysis %>%
  #    select(any_of(c(vx, vy, vx_runchart))) %>% 
  #    pivot_longer(cols = !!as.symbol(vx)) %>% 
  #    filter(!(
  #      is.na(value) | is.na(!!as.symbol(vy))
  #      )
  #    )
  
  function_title(vtitle = vx_txt, vheader_level = vheader_level)
  
  cat("The following plot introduces the results of '", vy_txt,"' colored by '", vx_runchart_txt, "'.\n\n")
  
  function_title(vtitle = "Descriptive analysis", vheader_level = vheader_level + 1)

  function_title(vtitle = "Run chart", vheader_level = vheader_level + 2)
  
  prunchart_one_parameter <- runchart_function(
      dfunc_runchart = dfunc_quali_one_analysis,
      vx_runchart = vx_runchart,
      vy_runchart = vy,
      vmanufacturing_date = vmanufacturing_date,
      vcolor_runchart = vx,
      vfacetx_runchart = ".",
      vfacety_runchart = ".",
      bool_show_color_legend = F,
      bool_facet_scale = "free_y",
      vtitle = paste0("Run chart of ", vy_txt, " colored by\n", vx_txt),
      vntick = vntick
  )
  
  plot(prunchart_one_parameter)
  cat("\n\n")
  

  # function_title(vtitle = "Scatterplot", vheader_level = vheader_level + 2)
  # 
  # pscatter_plot <- ggplot(data = dfunc_melt_child %>% 
  #                            mutate(
  #                              name = gsub("_", " ", name),
  #                              value = gsub("_", " ", value)
  #                              ), 
  #                          aes_string(x = "value", y = vy, 
  #                                      group = "value", color = "value")) + 
  #      geom_violin(alpha = 0.1, linewidth = 0.2, show.legend = F) + 
  #      geom_jitter(height = 0, width = 0.2, show.legend = F) + 
  #      theme_plot + 
  #      facet_grid(~name) + 
  #      ggtitle(paste0("Scatterplot of ", vy_txt, "\nby levels of ", vx_txt)) +
  #    ylab(vy_txt)
  # 
  # plot(pscatter_plot)
  # cat("\n\n")
  
  function_title(vtitle = "Model", vheader_level = vheader_level + 2)

  function_title(vtitle = "Homogeneity of Variance Between Groups", vheader_level = vheader_level + 2)
  
  df_model <- dfunc_quali_one_analysis %>%
    # filter(!(is.na(!!as.symbol(vx)) | is.na(!!as.symbol(vy)))) %>%
    mutate(!!as.symbol(vx) := factor(!!as.symbol(vx), levels = unique(!!as.symbol(vx))))
  
  cat("The homogeneity of variance between groups is assessed via a Levene test.\n\n")
  vformula <- as.formula(paste(vy, "~ ", vx))
  # res_levene <- leveneTest(vformula, data = df_model)
  # 
  # invisible(print_summary_loop(res_levene))
  # cat("\n\n")
  
  # levene_pval <- res_levene$`Pr(>F)`[1]
  # if(levene_pval <= 0.05){
  # cat("The Levene test shows significant difference of variability between groups.\n\n")
  # }
  # if(levene_pval > 0.05){
  #   cat("The Levene test did not detect significant difference of variability between groups.\n\n")
  # }
  
  function_title(vtitle = "Model outputs", vheader_level = vheader_level + 2)
  
  function_title(vtitle = "Summary", vheader_level = vheader_level + 3)
  
  cat("The obtained values are:\n")
  
  m <- lm(formula = vformula, data = df_model)
  s <- summary(m)
  invisible(print_summary_loop(s))
  cat("\n\n")
    
  cat("The confidence intervals can be plotted:\n") 
  df_confint <- lsmeans::lsmeans(m, vx) %>% 
      as.data.frame() %>% 
      clean_names() %>% 
      rename("modality" = vx) %>% 
      arrange(lsmean) %>% 
      mutate(modality=factor(modality, levels = unique(modality))) 
  
  pconfint <- ggplot(df_confint, aes(x = lsmean, y = modality)) + 
    geom_point() + 
    geom_errorbar(
      aes(xmin = lower_cl, xmax = upper_cl, 
        color = modality), width = 0.2) +
    geom_point(data = df_model, 
               aes_string(x = vy, y = vx, color = vx)) +
    theme_plot + 
    geom_label(aes(label = round_half_up(lsmean, 1))) + 
    ggtitle(paste("Estimated least mean squares and associated 95% confidence",
                  "\nby the model")) 
  
  plot(pconfint)
  cat("\n\n")
  
  # function_title(vtitle = "Hypotheses checking", vheader_level = vheader_level + 3)
  # 
  # cat("Test for detecting violation of normality assumption: \n")
  # list_resid_normality <- ols_test_normality(m)
  # list_resid_normality

}

root_univariate_qualitative = function(
    dfunc_univ_quali = NULL,
    vy = NULL,
    vx_runchart = col_id, # Uses config variable
    vparams_id = NULL,
    vparam_qualitative  = NULL, 
    vheader_level = 2,
    vntick = 5,
    vmanufacturing_date = col_date, # Uses config variable
    vcolor_runchart = NULL
){

  # --------------------------------------------------------- #
  # Dataset preparation
  # --------------------------------------------------------- #
  df_univariate_quali <- dfunc_univ_quali %>% 
    select(any_of(c(vparams_id, vparam_qualitative, vy))) 
  
  df_melt <- df_univariate_quali %>%  
    pivot_longer(cols = -any_of(c(vparams_id, vy))) %>% 
    group_by(name) %>% 
    filter(!is.na(value)) %>%
    filter(!(n_distinct(value) == n())) %>%
    filter(!n_distinct(value) == 1) %>% 
    ungroup()

  vparam_quali_func <- df_melt %>% distinct(name) %>% pull() %>% sort()
  
  # --------------------------------------------------------- #
  # Initialisation
  # --------------------------------------------------------- #
  vy_txt <- func_clean_title(vy)
  vx_runchart_txt <- func_clean_title(vx_runchart)
  
  # --------------------------------------------------------- #
  # Overall plot
  # --------------------------------------------------------- #
  
  function_title(vtitle = "Overall plot", vheader_level = vheader_level)

  # Divide parameters in groups of 5 
  group_size <- 3
  group_list <- split(vparam_quali_func, ceiling(seq_along(vparam_quali_func)/group_size))

  for(i in seq_along(group_list)){

    vars_subset <- group_list[[i]]

    prunchart_quali <- runchart_function(
      dfunc_runchart = df_melt %>% filter(name %in% vars_subset) %>% mutate(name = gsub("_", " ", name)),
      vx_runchart = vx_runchart,
      vy_runchart = vy,
      vmanufacturing_date = vmanufacturing_date,
      vcolor_runchart = "value",
      vfacetx_runchart = ".",
      vfacety_runchart = "name",
      bool_show_color_legend = F,
      bool_facet_scale = "free_y",
      vtitle = paste0("Run chart of\n", vx_runchart_txt, " – Group ", i, "/", length(group_list)),
      vntick = vntick
    ) +
      theme(
        strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 6)
      )

    knitr::opts_chunk$set(fig.height = max(6, length(vars_subset) * 3.2))
    print(prunchart_quali)
    knitr::opts_chunk$set(fig.height = 6)

    cat("\n\n")
  }



  
  # --------------------------------------------------------- #
  # Apply function for each of the quantitative parameter
  # --------------------------------------------------------- #
  function_title(vtitle = "Analysis by parameter", vheader_level = vheader_level)
  
  for(j in 1:length(vparam_quali_func)){
    
    # j <- 6
    # vx <- vparam_quali_func[j]
    
    qualitative_analysis_one_parameter(
      dfunc_quali_one_analysis = df_univariate_quali,
      vx = vparam_quali_func[j],
      vy = vy,
      vx_runchart = vx_runchart,
      vcolor_runchart = vcolor_runchart,
      vheader_level = vheader_level + 1,
      vmanufacturing_date = vmanufacturing_date
    )
    
    cat("\n\n")
    
  }
  
}

```



```{r global_function}

global_function = function(
    dfunc = df_analysis, 
    vy = NULL,
    vcolor_runchart = NULL,
    vparams_id = NULL,
    vx_runchart = NULL,
    vparam_quantitative = NULL,
    vparam_qualitative = NULL,
    vheader_level = 2,
    vntick = 5
){
  
  # --------------------------------------------------------- #
  # Initialisation
  # --------------------------------------------------------- #
  # --------------------------------------------------------- #
  # Univariate analyses
  # --------------------------------------------------------- #
  function_title(vtitle = "Univariate analyses", vheader_level = vheader_level + 1)
  
  # --------------------------------------------------------- #
  # Univariate analyses : quantitative
  # --------------------------------------------------------- #
  if(!is.null(vparam_quantitative)){
    
    function_title(vtitle = "Quantitative parameters", vheader_level = vheader_level + 2)
  
    root_univariate_numeric(
      dfunc_univ_quanti = dfunc,
      vy = vy,
      vx_runchart = vx_runchart,
      vcolor_runchart = vcolor_runchart,
      vparams_id = vparams_id, 
      vparam_quantitative = vparam_quantitative,
      vheader_level = vheader_level + 3,
      vntick = vntick
    )
    
  }

  # --------------------------------------------------------- #
  # Univariate analyses : qualitative
  # --------------------------------------------------------- #
  if(!is.null(vparam_qualitative)){
    
    function_title(vtitle = "Qualitative parameters", vheader_level = vheader_level + 2)
  
    root_univariate_qualitative(
      dfunc_univ_quali = dfunc,
      vy = vy,
      vx_runchart = vx_runchart,
      vcolor_runchart = vcolor_runchart,
      vparams_id = vparams_id , 
      vparam_qualitative = vparam_qualitative,
      vheader_level = vheader_level + 3,
      vntick = vntick,
      vmanufacturing_date = col_date # Passed from config
    )
    
  }

  # function_title(vtitle = "Multivariate analyses", vheader_level = vheader_level + 1)
  
}

```



```{r global_param_initilisation}

# Parameters initialized dynamically from configuration above
vparams_id <- c(
  col_id,
  col_date
)

vparam_quantitative <- df_analysis %>% 
  select(where(is.numeric)) %>% 
  colnames()

vparam_qualitative <- df_analysis %>% 
  select(where(is.character)) %>% 
  colnames()

```

```{r global_function_execution, results='asis'}

# Arguments now use the dynamic variables (vx_runchart, etc)
# which were set in 'definition_for_rest_of_the_script' based on config

global_function(
    dfunc = df_analysis, 
    vy = vy,
    vparams_id = vparams_id,
    vx_runchart = vx_runchart,
    vcolor_runchart = NULL,
    vparam_quantitative = vparam_quantitative,
    vparam_qualitative = vparam_qualitative,
    vheader_level = 1,
    vntick = 5
)

```


# Appendix

## R session

This report was generated with this setting :

```{r}
sessionInfo()
```

## Date of report generation

This report was generated at `r now()`.